\section*{\textcolor{orangebold}{前言}}

\indent {
	Avali及其相关的传说和概念属于其创作者RyuujinZERO的所有。
	虽然本书基于这一主题，但不应将其视为官方的传说。
	本书旨在将Ryuujin所编写和讨论的Avali传说中的原则和概念汇集到一个地方。
	此外，本书的作者、编辑、艺术家以及参与者们仔细地精炼并进一步发展了这些传说，扩展了已建立的内容。
	由于这一点，几乎所有的原创概念保持不变，仅有两处重大修改。
	Avali的核心温度从-30°C调整为-7°C，他们的体内溶剂变成了氨水混合物。
	这一修改是为了为Avali提供更好的操作温度范围，将他们从接近纯氨的沸腾范围中推出来，避免纯水导致的冻结。
	此外，这一改变还带来了更高效的能量传输，部分得益于增加的热量。
}

\indent {
	This book was written, illustrated,
	edited, and reviewed by volunteer members
	who admire and are interested in its respective
	concepts. While the original creator did not
	participate in the development and
	implementation of some of the topics in the
	book, all subjects discussed in the book are
	made with the creator’s ideas and wishes in
	mind, and we worked tirelessly within the
	established parameters of the original concepts.
}

\indent \st {
	The book is a living document. The
	topics discussed within the can will be subject
	to change or removal. Alterations will be
	identified within the guide with a bold black line
	(see example on the side) within the margin of
	the page, either on the left or right side of the
	affected paragraph. A summary of changes will
	also be provided, located before the Table of
	Contents. Version numbers go in ascending
	order, starting at 0. All previous editions will
	become obsolete after the most up-to-date
	edits are released. The version edition is located
	at the top left-hand corner of each page. This
	document has two variants: a public edition and
	a supporter edition. Each version will be
	identified with a two-letter code at the end of
	the edition number, either a “PE” or a “SE,”
	respectively. Draft editions will be identified
	with a “D” at the end of the version edition
	identifier code. The publication date is located
	at the top right-hand corner of the page.
}
