\section*{\textcolor{orangebold}{前言}}

\begin{TranslatorNoteBox}
	由于本书有大量口语化和非母语为英语作者编写的内容，

	译者在翻译过程中进行了大量的重组及根据自己的理解进行润色。
\end{TranslatorNoteBox}

Avali及其相关的设定和概念属于其创作者 RyuujinZERO 所有。虽然本书是基于该内容撰写的，但你不应将其视为官方设定。
本书旨在将 Ryuujin 本人已公开阐述的 Avali 原始设定与核心概念系统整理成册。此外，本书的作者、编辑、插画师及全体参与者都在已经建立的基础上仔细完善和扩展。
由于本书的特殊性质，几乎所有原始概念都保持不变，仅有两处重大修改：Avali 的核心温度从-30℃调整为-7℃，并且体液改为了氨水混合物。
这么做是为了扩大 Avali 的适宜活动温度范围，避免纯氨沸腾和纯水结冰。此外，该调整还带来了额外的优势：由于混合体液提升了整体温度，能量传递效率也因此显著提高。

本书由 Avali 爱好者组成的志愿者团队志愿完成，涵盖撰稿、插画、编辑和审校等工作。
While the original creator did not participate in the development and implementation of some of the topics in the book, all subjects discussed in the book are made with the creator’s ideas and wishes in mind, and we worked tirelessly within the established parameters of the original concepts.

\st {
	The book is a living document. The
	topics discussed within the can will be subject
	to change or removal. Alterations will be
	identified within the guide with a bold black line
	(see example on the side) within the margin of
	the page, either on the left or right side of the
	affected paragraph. A summary of changes will
	also be provided, located before the Table of
	Contents. Version numbers go in ascending
	order, starting at 0. All previous editions will
	become obsolete after the most up-to-date
	edits are released. The version edition is located
	at the top left-hand corner of each page. This
	document has two variants: a public edition and
	a supporter edition. Each version will be
	identified with a two-letter code at the end of
	the edition number, either a “PE” or a “SE,”
	respectively. Draft editions will be identified
	with a “D” at the end of the version edition
	identifier code. The publication date is located
	at the top right-hand corner of the page.
}

If you, the reader, discover an issue or
have a concept that you believe would fit within
the lore guide, you can submit your idea to the
creators of this book, and it will be reviewed.
This does not guarantee the inclusion or
certification of your concepts in the guide.
Alterations made outside of the will of the
author, illustrators, or editors are strictly
prohibited.

Thank you for taking the time and
reading our product. We hope you find it
informative and insightful on the subject at
hand. Once again, we would like to reiterate
that this is NOT official lore.

\clearpage
